Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-21 paper/v2/paper-edited.tex
fix in algorithm
fix algorithm numbering bug. Edit conclusion

\begin{algorithm}[t!]
\caption{Inferring regret-free preferences}
\label{alg:failures}
\begin{algorithmic}[1]
\Procedure{Regret-free($G$, $N_1$, $N_2$)}{}
  \If {$N_1 \not\approx N_2$} \Return false
  \EndIf
  \State $q \gets Queue()$
  \State $q.Enqueue (N_1, N_2)$
  \While {$!q.Empty()$}
    \State $(n_1,n_2) \gets q.Dequeue()$
    \If {$n_1 \nleq_{rank} n_2$}
      \Return false
    \EndIf
    \For {$n_2'$ in adj($G$, $n_2$)}
      \If {\big($\exists n_1' \in \textup{adj}(G,n_1), n_1' \approx n_2'$\big) \textbf{or} \\
            \hspace{5.2em} 
            \big($\exists n_1' \in$ $G$, dominates $n_1$, $n_1' \approx n_1$\big)}
        \If {$(x,y)$ not marked}
          \State {mark $(x,y)$ as seen}
          \State $q.Enqueue(x,y)$
        \EndIf
      \Else { \Return $false$}
      \EndIf
    \EndFor
  \EndWhile
  \Return true
  \EndProcedure
\end{algorithmic}
\end{algorithm}

@@

We introduced \sysname, a language and compiler for implementing network-wide policies using a distributed set of devices running BGP. Propane allows operators to describe their policy naturally through high-level constraints on the shape and relative preferences of paths for different types of traffic. When \sysname compiles a policy, the resulting BGP configurations are correct-by-construction and faithfully implement the policy in a distributed fashion, regardless of the number and combinations of failures. Applying \sysname to real-world networks showed that its language is expressive and its compiler is scalable.

>>>>

\begin{algorithm}[t!]
\caption{Inferring regret-free preferences}
\label{alg:failures}
\begin{algorithmic}[1]
\Procedure{Regret-free($G$, $N_1$, $N_2$)}{}
  \If {$N_1 \not\approx N_2$} \Return false
  \EndIf
  \State $q \gets Queue()$
  \State $q.Enqueue (N_1, N_2)$
  \While {$!q.Empty()$}
    \State $(n_1,n_2) \gets q.Dequeue()$
    \If {$n_1 \nleq_{rank} n_2$}
      \Return false
    \EndIf
    \For {$n_2'$ in adj($G$, $n_2$)}
      \If {\big($\exists n_1' \in \textup{adj}(G,n_1), n_1' \approx n_2'$\big) \textbf{or} \\
            \hspace{5.2em} 
            \big($\exists n_1' \in$ $G$, dominates $n_1$, $n_1' \approx n_1$\big)}
        \If {$(n_1',n_2')$ not marked}
          \State {mark $(n_1',n_2')$ as seen}
          \State $q.Enqueue(n_1',n_2')$
        \EndIf
      \Else { \Return $false$}
      \EndIf
    \EndFor
  \EndWhile \\
  \hspace{\algorithmicindent} \Return true
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

We introduced \sysname, a language and compiler for implementing network-wide policies using a distributed set of devices running BGP. Propane allows operators to describe their policy through high-level constraints on the shape and relative preferences of paths for different types of traffic. When \sysname compiles a policy, the resulting BGP configurations are guaranteed to faithfully implement the policy in a distributed fashion, regardless of any number of network failures. Applying \sysname to real-world networks showed that its language is expressive and its compiler is scalable.
